Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2022-10-18 src/tex/appendicies.tex
fix bug
add ffig

\begin{figure*}[ht!]
    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
    \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model. The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.
    \label{fig:ppc}
    \script{plot_ppcs.py}
\end{figure*}

We follow the posterior predictive checking procedure done in recent population studies to validate our models inferences \citep{o3a_pop,Edelman_2022ApJ}. 
For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in \ref{fig:ppc}. When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
    \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model. The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.}
    \label{fig:ppc}
    \script{plot_ppcs.py}
\end{figure}

We follow the posterior predictive checking procedure done in recent population studies to validate our models inferences \citep{o3a_pop,Edelman_2022ApJ}. 
For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in figure \ref{fig:ppc}. When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.
